\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{\protect\numberline{}{参考文献}\hfil}
\markboth{\bibname}{参考文献}

% 2_introduction
\bibitem{cobe}
\href{D. J. Fixsen and E. S. Cheng and J. M. Gales and J. C. Mather and R. A. ShaFer and E. L. Wright. The cosmic microwave background spectrum from the full cobe firas data set. The Astrophysical Journal, 473(2):576, 1996.}{
D. J. Fixsen and E. S. Cheng and J. M. Gales and J. C. Mather and R. A. ShaFer and E. L. Wright. The cosmic microwave background spectrum from the full cobe firas data set. The Astrophysical Journal, 473(2):576, 1996.
}

\bibitem{cmb_discovery}
\href{https://ui.adsabs.harvard.edu/abs/1965ApJ...142..419P/abstract}{
A. A. Penzias, R. W. Wilson. A Measurement of Excess Antenna Temperature at 4080 Mc/s. {\it Astrophysical Journal}, vol.142, p.419–421, 1965.
}

\bibitem{cmb_discovery_theory}
\href{https://ui.adsabs.harvard.edu/abs/1965ApJ...142..414D/abstrac}{
R. H. Dicke, P. J. E. Peebles, P. G. Roll, D. T. Wilkinson. Cosmic Black-Body Radiation. {\it Astrophysical Journal}, vol.142, p.414–419, 1965.
}


\if0
\bibitem{wmap}
\href{https://map.gsfc.nasa.gov/}{
https://map.gsfc.nasa.gov/
}
\fi

\bibitem{shonda_spie}
\href{https://www.spiedigitallibrary.org/conference-proceedings-of-spie/11445/114457Q/On-site-performance-of-GroundBIRD-a-CMB-polarization-telescope-for/10.1117/12.2560918.short}
{S.Honda, et al., On-site performance of GroundBIRD, a CMB polarization telescope for large angular scale observations. Proceedings Volume 11445, Ground-based and Airborne Telescopes VIII; 114457Q (2020)}


\bibitem{plank}
\href{https://www.aanda.org/articles/aa/full\_html/2020/09/aa33880-18/aa33880-18.html}
{Planck Collaboration, Plank 2018 results. 1.Overview and the cosmological legacy of Planck. Astronomy \& Astrophysics, 2018.}

\bibitem{sato}
\href{https://ui.adsabs.harvard.edu/abs/1981MNRAS.195..467S/abstract}
{K. Sato. First-order phase transition of a vacuum and the expansion of the universe. Monthly Notices of the Royal Astronomical Society, Vol 195:pp.467–479, 1981.}


\bibitem{gwave}
\href{https://arxiv.org/abs/1605.01615}
{Maria Chiara Guzzetti, et al., Gravitational waves from inflation.}

\bibitem{n_mass}
\href{https://journals.aps.org/prd/abstract/10.1103/PhysRevD.92.123535}{
  R. Allison, P. Caucal, E. Calabrese, J. Dunkley, and T. Louis, Towards a cosmological neutrino mass detection. Phys. Rev. D 92, 123535, 2015.
}

% 3_MKID
\bibitem{high_eff}
\href{https://aip.scitation.org/doi/10.1063/1.4829657}{
  R. M. J. Janssen, et al., High optical efficiency and photon noise limited sensitivity of microwave kinetic inductance detectors using phase readout. Appl. Phys. Lett. 103, 203503, 2013.
}

\bibitem{microwave_eng}
D. M. Pozar. Microwave Engineering. John Wiley \& Sons, Inc., Hoboken, New Jersey, 2012.

\bibitem{BCS}
\href{https://journals.aps.org/pr/abstract/10.1103/PhysRev.108.1175}
{J. Bardeen, L. N. Cooper, and J. R. Schrieffer. Theory of superconductivity. Physical
Review, 108:1175, 1957.
}

\bibitem{fremi_dense}
\href{G. Vardulakis. Superconducting kinetic inductance dectectors: theory, simulations and
experiments. University of Cambridge, Cambridge, UK, 2007.}
{G. Vardulakis. Superconducting kinetic inductance dectectors: theory, simulations and
experiments. University of Cambridge, Cambridge, UK, 2007.
}

\bibitem{n0}
\href{https://journals.aps.org/prb/abstract/10.1103/PhysRevB.14.4854}
{S. B. Kaplan, C. C. Chi, D. N. Langenberg, J. J. Chang, S. Jafarey, et al. Quasiparticle
and phonon lifetimes in superconductors. Physical Review, B14:4854, 1976.
}

\bibitem{res_omega}
Neil W. Ashcroft, N. David Mermin. Solid State Physics

\bibitem{London}
\href{F. London and H. London. The electromagnetic equations of the supraconductor.
Proceedings of the Royal Society of London Series A, 149:71, 1935.
}{F. London and H. London. The electromagnetic equations of the supraconductor.
Proceedings of the Royal Society of London Series A, 149:71, 1935.
}

\bibitem{MS_theo}
\href{D. Mattis and J. Bardeen. Theory of the anomalous skin effect in normal and super-
conducting metals. Physical Review Letters, 111:412, 1958.}
{D. Mattis and J. Bardeen. Theory of the anomalous skin effect in normal and super-
conducting metals. Physical Review Letters, 111:412, 1958.}

\bibitem{gao}
\href{https://resolver.caltech.edu/CaltechETD:etd-06092008-235549}{
J. Gao. The Physics of Superconducting Microwave Resonators. PhD thesis, California Institute of Technology Pasadena, California, 2008.
}

\bibitem{pieter}
\href{https://doi.org/10.4233/uuid:eae4c9fc-f90d-4c12-a878-8428ee4adb4c}{
P. J. de Visser. et al., Quasiparticle dynamics in aluminium superconducting microwave resonators. PhD thesis, Delft University of Technology, Delft, The Netherlands, 2014. 
}


% 4_MKIDkyoto
\bibitem{vac_pump}
\href{http://www.hakuto-vacuum.jp/pfeiffer\_vacuum/pdf/PumpingStation/HiCubeClassic.pdf}{
http://www.hakuto-vacuum.jp/pfeiffer\_vacuum/pdf/PumpingStation/HiCubeClassic.pdf}

\bibitem{ptc}
\href{https://www.cryomech.com/products/pt407/}{
https://www.cryomech.com/products/pt407/}

\bibitem{LNA}
\href{https://www.lownoisefactory.com/products/cryogenic/lnc-4-8-ghz/}{
https://www.lownoisefactory.com/products/cryogenic/lnc-4-8-ghz/}

\bibitem{vac}
\href{https://www.pfeiffer-vacuum.com/productPdfs/PTT03140010.en.pdf}{
https://www.pfeiffer-vacuum.com/productPdfs/PTT03140010.en.pdf  
}

\bibitem{thermo}
\href{https://www.toyo.co.jp/material/products/detail/rx.html}{
https://www.toyo.co.jp/material/products/detail/rx.html
}

\bibitem{lackshore372}
\href{https://www.toyo.co.jp/material/products/detail/372.html}{
https://www.toyo.co.jp/material/products/detail/372.html
}

\bibitem{deshima_exp}
\href{http://deshima.ewi.tudelft.nl/}{
  http://deshima.ewi.tudelft.nl/
}

\bibitem{deshima}
\href{https://www.spiedigitallibrary.org/journals/Journal-of-Astronomical-Telescopes-Instruments-and-Systems/volume-5/issue-03/035004/Wideband-on-chip-terahertz-spectrometer-based-on-a-superconducting-filterbank/10.1117/1.JATIS.5.3.035004.full}{
A Endo, et al.. “Wideband on-chip terahertz spectrometer based on a superconducting filterbank“ J. of Astronomical Telescopes, Instruments, and Systems, 5(3), 035004, 2019.
}

\bibitem{deshima_image}
\href{http://aste.nao.ac.jp/pressrelease/2019deshima/index.html}{http://aste.nao.ac.jp/pressrelease/2019deshima/index.html}

\bibitem{ikemitsu}
池満拓司. CMB望遠鏡のデータ読み出しシステムの時刻同期と較正に関する開発研究. 京都大学理学研究科 修士論文 2020.

\bibitem{ishitsuka}
石塚光. 超伝導検出器 MKID の周波数多重読み出し用 フロントエンド回路の開発. 総合研究大学院大学 高エネルギー加速器科学研究科 修士論文 2020.

\bibitem{welch}
\href{https://docs.scipy.org/doc/scipy/reference/generated/scipy.signal.welch.html}{
https://docs.scipy.org/doc/scipy/reference/generated/scipy.signal.welch.html
}

\bibitem{kutsuma}
沓間弘樹. CMB偏光観測にむけた超伝導検出器”MKID”のノイズ低減法の研究開発. 東北大学理学研究科 修士論文 2018.

\bibitem{kutsuma1}
\href{https://aip.scitation.org/doi/10.1063/1.5110692}{
H. Kutsuma, et al., A measurement method for responsivity of microwave kinetic inductance detector by changing power of readout microwaves. Appl. Phys. Lett. 115, 032603, 2019.
}

\bibitem{kutsuma2}
\href{https://aip.scitation.org/doi/10.1063/5.0013946}{
H. Kutsuma, Y.Sueno, et al., A method to measure superconducting transition temperature of microwave kinetic inductance detector by changing power of readout microwaves. AIP Advances 10, 095320, 2020.
}

% 5_TLS
\bibitem{TLS_review}
\href{https://arxiv.org/abs/2006.04718}{
  C. R. H. McRae, et al., Materials loss measurements using superconducting microwave resonators. Review of Scientific Instruments 91, 091101, 2020.
}

\bibitem{kumar}
\href{https://aip.scitation.org/doi/pdf/10.1063/1.2894584?casa_token=wSixfQUGxAUAAAAA:CPs8YHoWwOGIVSeqJLakFz0-GQ9TLncU8veuICWpfjPBgZYTjr-WcUaiIv0cPRtaopytECg_taMS}{
  Shwetank Kumar, et al., Temperature dependence of the frequency and noise of superconducting coplanar waveguide resonators. Appl. Phys. Lett. 92, 123503, 2008.
}

\bibitem{rami_fexp}
\href{https://aip.scitation.org/doi/full/10.1063/1.3467052}
{R. Barends, Reduced frequency noise in superconducting resonators. Appl. Phys. Lett. 97, 033507, 2010.}

\bibitem{hybrid}
\href{https://arxiv.org/pdf/0909.2060.pdf}
{Omid Noroozian, et al., Two-level system noise reduction for Microwave Kinetic Inductance Detectors, }

\bibitem{kutsuma_D}
Hiroki Kutsuma ph.D thesis.

\bibitem{rami_cpw}
\href{https://aip.scitation.org/doi/10.1063/1.3458705}
{R. Barends, Minimal resonator loss for circuit quantum electrodynamics. Appl. Phys. Lett. 97, 023508, 2010.}

  
\end{thebibliography}